### 2021-03-12 paper_1.tex
1.4.5

>>>>

\subsubsection{\emph{Extended Saliency-Related Applications}}
The peculiarity of the proposed method also lies in the search for salient 
edges. This process is possible by replacing the four color components with 
three luminance gradients and two color-opponent channels. The system also 
proves to be capable of being able to detect text as well.
